\section{Theory}
\label{sec:theory}
In this miniproject, the application of Fourier, dB, smoothing, zeropadding, windowing and energy will be performed, but first a quick glanse at the theory behind it all.

\subsection{Fourier}

Fourier is a method for getting a signal from the time domain into the frequency domain. 
For a fourier function a signal go from $x(t) \rightarrow X(f)$. Fourier is defined by:

\begin{equation}
X(f) = \int_{-\infty}^{\infty} x(t)e^{-j2\pi ft}dt
\end{equation}

where $x(t)$ is some continous signal \cite[p. 53]{DSP}. 
When a fourier transform is needed in MATLAB, the "fft" function can be used. 
"fft" stands for "fast fourier transform". 
The "fft" function computes the discrete fourier transform (DFT) of some signal by using a fast fourier transform algorithm \cite[fft]{MATLAB_DOC}. 
By default "fft" only take one parameter, which is the signal:

\begin{minted}{matlab}
	Y = fft(y)
\end{minted}

\subsection{The dB-scale}

The \SI{}{\decibel} scale is used for plotting signals in the frequency domain and is deducted from the bel scale. 
The bel scale is defined by the base 10 logarithm of the difference between two powers\cite[Appendix E]{DSP}

\[
\log_{10}\frac{P1}{P2}\SI{}{\bel}
\] 

The bel scale itself can be very big which led to the unit decibel, that is one tenth of a bel:

\begin{equation}
10\log_{10}\frac{P1}{P2}\SI{}{\decibel}
\end{equation}

This can also be used in combination of a function, which when applied to $X(m)$ gives:

\begin{equation}
X_{\SI{}{\decibel}}(m) = 10\log_{10}(|X(m)|^2)\SI{}{\decibel} = 20\log_{10}(|X(m)|)\SI{}{\decibel}
\end{equation}

\subsection{Smoothing}

When using Matlab, the "smooth" function takes a column vector and smoothesn the data by making averages of a defined span, which by default is 5 datapoints \cite[smooth]{MATLAB_DOC}. 
For this project the default value has been used, hence the prototype for the function is:

\begin{minted}{matlab}
	Y_smooth = smooth(Y)
\end{minted}
If another span value is needed the prototype for smooth is:

\begin{minted}{matlab}
	Y_smooth = smooth(Y, span_value)
\end{minted}

The smooth function is great for getting a better overview of data with many different values, becuase of the averages it makes. 

\subsection{Zero Padding}
Zero padding is a way of getting more frequency bins hence getting a better visual representation of the signal. 
To do zero padding, a series of 0's are appended to the end of the signal, afterwards the discrete fourier transform is performed. 
Example code of zero padding the signal from a car motor in Matlab is seen below:

\begin{minted}{matlab}
	[y,Fs] = audioread('./car.wav'); % load the data
	y_zpad = cat(1, y, zeros(N, 1)); % append zeros
	Y_zpad = fft(y_zpad); % Do fft
\end{minted}

\subsection{Windowing}
\label{sec:windowing}
Window functions are made for reducing leakage, which can be induced during DFT, when peforming fft on signals, which does not have a clear start and end. If we have an input sequence of $x(n)$ and a window function $w(n)$, where $N$ is the sum of all samples, $n$ is a given sample, the formula of any window function is

\begin{equation}
\label{eq:window}
X_w(m) = \sum_{n=0}^{N-1} w(n)\cdot x(n)e^{\frac{-j2\pi nm}{N}}
\end{equation}

In \cref{sec:analysis} the Hamming window is used, which has the following formula

\begin{equation}
\label{eq:hamming}
w(n) = 0.54-0.46\cos\left(\frac{2\pi n}{N}\right)
\end{equation}

\subsection{Energy}
Later on when the different functions just described in this section is applyied, the energy of a signal is not always the same before and after. When doing the Fourier transform, the Parceval's theorem (\cref{eq:pars}) ensures that the energy before and after are the same, when applying smooth this is not the case.

\begin{equation}
	\sum_{n=0}^{N-1}\left|x\left[n\right]\right|^2=\frac{1}{N}\sum_{k=0}^{N-1}\left|X\left[k\right]\right|^2
	\label{eq:pars}
\end{equation}